%-------------------------
% Resume in Latex
% Author : Mohammad Abdul Ahad Chowdhury
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[12pt,a4paper]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage[margin=2cm,footskip=0.75cm]{geometry}
\usepackage{lastpage}
% \usepackage[UKenglish]{isodate}
\usepackage[ddmmyyyy]{datetime}

\usepackage{tikz}

\newcommand{\ExternalLink}{%
    \tikz[x=1.2ex, y=1.2ex, baseline=-0.05ex]{% 
        \begin{scope}[x=1ex, y=1ex]
            \clip (-0.1,-0.1) 
                --++ (-0, 1.2) 
                --++ (0.6, 0) 
                --++ (0, -0.6) 
                --++ (0.6, 0) 
                --++ (0, -1);
            \path[draw, 
                line width = 0.5, 
                rounded corners=0.5] 
                (0,0) rectangle (1,1);
        \end{scope}
        \path[draw, line width = 0.5] (0.5, 0.5) 
            -- (1, 1);
        \path[draw, line width = 0.5] (0.6, 1) 
            -- (1, 1) -- (1, 0.6);
    }
}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\usepackage{setspace}
\onehalfspacing % 1.5 line spacing

% \renewcommand{\headrulewidth}{0pt} % no line in header area
% \fancyfoot{} % clear all footer fields
\fancyfoot[LO,LE]{\footnotesize \color{lightgray} The latest version of this document is available at \href{https://pia.sh/resume}{\underline{pia.sh/resume} \ExternalLink}.}
\fancyfoot[RO,RE]{\footnotesize \color{lightgray}\textit{\small page \thepage{} of \pageref*{LastPage}}}

\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
  \item\small{{#1 #2 #3 #4 \vspace{-2pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
  \vspace{-7pt}
  \item
  \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
    \small#1 & \small #2\\
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]\itemsep0.75em}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}\itemsep0.2em}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\usepackage[document]{ragged2e}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
  {\Huge \scshape Mohammad Abdul Ahad Chowdhury} \\ \vspace{5pt}
  % AWS Certified Solutions Architect •
  Full-Stack Web Developer • Machine Learning and Big Data Enthusiast \\ \vspace{5pt}
  \small \href{mailto:ahad@maacpiash.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ahad@maacpiash.com}} ~ \href{https://www.maacpiash.com}{\raisebox{-0.2\height}\faGlobe\ \underline{www.maacpiash.com}} ~ \href{https://github.com/maacpiash}{\raisebox{-0.2\height}\faGithub\ \underline{maacpiash}} ~
  \href{https://linkedin.com/in/maacpiash}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/maacpiash}}
  \vspace{5pt}
\end{center}


% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Software Methodology
%                 \item Algorithms Analysis
%                 \item Database Management
%                 \item Artificial Intelligence
%                 \item Internet Technology
%                 \item Systems Programming
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd

\begin{justify}
A full-stack developer experienced in React.js, Node.js, ASP.NET Core, and machine learning. Worked on projects in civil registration, healthcare, and CRM systems. Skills include database management, cloud platforms such as AWS, and DevOps. Completed a Master of Data Science degree and pursuing AWS Solutions Architect certification.
\end{justify}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer}{April 2021 -- May 2022}
      {Apollo International}{Sydney, NSW, Australia}
      \\ \vspace{8pt} Responsible for developing the in-house CRM solution. \vspace{-4pt}
      \\ \vspace{6pt} Responsibilities: \vspace{-6pt}
      \resumeItemListStart
        \resumeItem{Collaborated closely with directors and both onshore and offshore teams to align business requirements and CRM system features with organisational goals.}
        \resumeItem{Completed the development of a high-performance frontend application using modern libraries and frameworks such as TypeScript, React.js, Redux.js, Next.js, Material UI (MUI), and Storybook.}
        \resumeItem{Architected and implemented a robust backend solution, including a user authentication service, utilising ASP.NET Core and Entity Framework Core.}
        \resumeItem{Managed relational and in-memory databases, leveraging PostgreSQL for persistent storage of relational entities and Redis for in-memory response caching and fast data access for user authentication to ensure high availability and quick response times.}
        \resumeItem{Integrated various third-party systems into the CRM, including lead collection from website contact forms and Facebook (Meta) Ads, to streamline marketing efforts.}
        \resumeItem{Conducted rigorous frontend testing with Jest, React Testing Library (RTL), and Playwright, ensuring high-quality, bug-free deliverables.}
        \resumeItem{Performed backend testing using xUnit and Moq to maintain integrity and reliability.}
        \resumeItem{Deployed applications to VPS environments, managing configurations of Nginx, PM2, and Certbot, and facilitated secure and stable deployments through SSH.}
        \resumeItem{Provided regular progress updates and strategic insights to the General Manager, ensuring alignment with organizational objectives and technical feasibility.}
        \resumeItem{Collaborated with cross-functional teams to identify CRM software enhancements and website improvements, delivering solutions that supported operational efficiency.}
        \resumeItem{Authored comprehensive end-user documentation, detailing operational procedures and system functionalities for seamless adoption by business users.}
        \resumeItem{Delivered ongoing maintenance, technical support, and system updates to ensure platform stability and address evolving business needs.}
        \resumeItem{Proposed and implemented continuous improvement initiatives to optimise system performance and expand functionalities.}
      \resumeItemListEnd

      \vspace{1.5em}

    \resumeSubheading
      {Junior Software Engineer}{February 2019 -- January 2020}
      {\href{https://www.dsinnovators.com}{Dynamic Solution Innovators Ltd. \ExternalLink}}{Dhaka, Bangladesh}
      \\ \vspace{8pt} Responsible for developing enterprise web applications, following agile (scrum) workflow. \vspace{1pt}\\
      % \\ \vspace{6pt}
      Projects:
      % The \href{https://www.opencrvs.org}{\underline{OpenCRVS} \ExternalLink} project (\href{https://www.dsinnovators.com/projects/open-crvs}{\underline{project details} \ExternalLink}, \href{https://www.dsinnovators.com/casestudies/open-crvs-2}{\underline{technical details} \ExternalLink}, \href{https://github.com/opencrvs/opencrvs-core/commits?author=maacpiash}{\underline{commits} \ExternalLink}) and the full-stack solution for \href{https://www.olwel.com}{\underline{Olwel} \ExternalLink}, a healthcare startup (\href{https://www.dsinnovators.com/projects/olwel}{\underline{project details} \ExternalLink}, \href{https://www.dsinnovators.com/casestudies/olwel-2}{\underline{technical details} \ExternalLink}).\\
      \vspace{-4pt}
      \resumeItemListStart
      \resumeItem{\href{https://www.opencrvs.org}{\underline{OpenCRVS}}, a solution for civil registration and vital statistics, backed by Plan International and the government of Bangladesh (\href{https://www.dsinnovators.com/casestudies/open-crvs-2}{\href{https://www.dsinnovators.com/projects/open-crvs}{\underline{project details}}, \underline{technical details}}).}
      \resumeItem{The full-stack solution for \href{https://www.olwel.com}{\underline{Olwel}}, a Finland-based healthcare startup providing telemedicine and at-home medical care services.(\href{https://www.dsinnovators.com/projects/olwel}{\underline{project details}}, \href{https://www.dsinnovators.com/casestudies/olwel-2}{\underline{technical details}}).}
      \resumeItemListEnd
      % \vspace{1pt}
      Responsibilities: \vspace{-6pt}
      \begin{itemize}
      \itemsep0.2em
        \resumeItem{\textit{OpenCRVS:}}
        \begin{itemize}
          \resumeItem{Engineered key frontend features and bug-fixes utilizing TypeScript, React.js, Redux.js, and Formik to deliver a responsive and user-friendly interface.}
          \resumeItem{Developed features and fixed bugs of scalable backend services using TypeScript, Node.js, Hapi.js, MongoDB, GraphQL, and Docker.}
          \resumeItem{Ensured code reliability through extensive unit testing with Jest}
          \resumeItem{Composed end-to-end tests with Cypress to guarantee predictable user experience.}
          \resumeItem{Refactored code to achieve target code coverage, improving maintainability.}
          \resumeItem{Collaborated with the scrum master and team members during sprint planning and daily stand-ups, aligning on goals and progress.}
        \end{itemize}
        \href{https://github.com/opencrvs/opencrvs-core/commits?author=maacpiash}{(\underline{commits on GitHub} \ExternalLink)}
        % \vspace{5em}
        \resumeItem{\textit{Olwel:}}
        \begin{itemize}
          \resumeItem{Contributed to frontend projects using React.js, Redux.js, Electron.js, and MUI.}
          \resumeItem{Contributed to backend services using Node.js, Hapi.js, RethinkDB, and AWS S3.}
          \resumeItem{Optimised RethinkDB queries by 20\%-50\%, reducing overall load times.}
          \resumeItem{Wrote comprehensive unit tests with Mocha to ensure system reliability.}
          \resumeItem{Developed database migration scripts to anonymize patient data for compliance with requirements of an external research project.}
          \resumeItem{Led dependency upgrades across the codebase, ensuring smooth transitions while preserving system stability.}
          \resumeItem{Innovated and executed new projects, including a medical prescription app for doctors, further expanding the platform's feature set.}
          \resumeItem{Regularly reported development progress and technical decisions to the CTO and business stakeholders, ensuring alignment with business objectives and timelines.}
        \end{itemize}
    \end{itemize}

    % \resumeSubheading
    %   {Research Assistant}{1 November 2016 -- 30 April 2018}
    %   {\href{https://www.northsouth.edu}{North South University}}{Dhaka, Bangladesh}
    %   \\ \vspace{8pt} Part-time employment under the Department of Environmental Science \& Management (\href{https://www.northsouth.edu/academic/shls/esm/}{\underline{website}}) for developing NODES, an airline management system (\href{http://www.ipsnews.net/2017/05/flying-green-in-bangladesh}{\underline{news article}}). \vspace{-6pt}
    %   \\ \vspace{6pt} Responsibilities: Development of the frontend of NODES with Windows Forms (.NET Framework).
    
  \resumeSubHeadingListEnd



%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Master of Data Science}{Aug 2023 -- September 2024}
      {Sydney Polytechnic Institute}{Sydney, NSW, Australia}
      \\ \vspace{0.1em} % WAM: 84.84\%.
      \item Capstone project: Investigation for Identification of the Most Effective Machine Learning
      Method for Credit Card Fraud Detection.
      % \\ Notable Coursework: Machine Learning and Data Mining, Data Visualisation and Tools, Natural Language Processing and Applications, Big Data Infrastructure and Processing, Artificial Intelligence and Innovation.
    \resumeSubheading
      {Bachelor of Science in Computer Science \& Eng.}{January 2014 -- August 2018}
      {North South University}{Dhaka, Bangladesh}
      \\ \vspace{0.8em} % CGPA: 2.98/4.00.
      Capstone project: Fruit Image Classification Using Convolutional Neural Networks (\href{https://www.igi-global.com/gateway/article/236206}{\underline{Publication}}).
      % \\ Notable Coursework: Software Engineering, Compiler Construction, Artificial Intelligence, Theory of Fuzzy Systems (\href{https://github.com/maacpiash?tab=repositories&q=CSE}{\underline{Repositories on GitHub}}).
  \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0in, label={}]
    \item{
     \textbf{Languages:}{ C\#, JavaScript, TypeScript, Python, SQL, C, R, \LaTeX.} \\
     \textbf{Backend:}{ ASP.NET Core, Entity Framework Core, Dapper, SignalR, Node.js, Express.js.} \\
     \textbf{Frontend:}{ Tailwind CSS, React.js, Redux.js, Next.js, Svelte, Astro, Blazor, PWA.} \\
     \textbf{Database:}{ MySQL, PostgreSQL, SQL Server, MongoDB, Redis, SQLite.} \\
     \textbf{Machine Learning:}{ Numpy, Pandas, Scikit-learn, Tensorflow/Keras.} \\
     \textbf{Big Data:}{ Apache Hadoop (HDFS, MapReduce, YARN), Apache Spark.}\\
     \textbf{DevOps:}{ Docker, CI/CD, SSH, Nginx.} \\
     \textbf{Platforms:}{ AWS (S3, EC2, ELB, Lambda, RDS, DynamoDB, SQS, SNS, SES), Azure App Service, PaaS (Vercel, Heroku).}
    }
 \end{itemize}
 
% %-----------PROFESSIONAL CERTIFICATIONS-----------
% \section{Certifications}
%   \resumeSubHeadingListStart
%   \resumeProjectHeading
%     {\textbf{AWS Certified Solutions Architect} $|$ \emph{Associate}}{SAA-C03}
%         % \begin{multicols}{2}
%             \begin{itemize}[itemsep=0em, parsep=3pt]
%                 \item Date of certification: 16 October 2024
%                 \item Date of expiration: 15 October 2027
%             \end{itemize}
%         % \end{multicols}
%         \vspace*{2.0\multicolsep}
%   \resumeSubHeadingListEnd
% \vspace{0.25pt}

% % -----------PROJECTS-----------
% \section{Projects}
%   \resumeSubHeadingListStart
%     \resumeProjectHeading
%       {\textbf{KonSchool} $|$ \emph{Recommendation system} $|$ \texttt{Blazor, MongoDB}}{\href{https://konschool.azurewebsite.net}{\underline{Azure} \ExternalLink} $|$ GitHub: \href{https://github.com/maacpiash/KonSchool}{\underline{KonSchool} \ExternalLink}}
%       \resumeItemListStart
%         \resumeItem{Fuzzy-AHP-based recommendation system for secondary schools in Bangladesh.}
%         \resumeItem{Status: completed, with unit and e2e tests at 95\% coverage.}
%         % \resumeItem{Another version is in development, with separate web APIs and a frontend developed with Blazor.}
%       \resumeItemListEnd
%       \vspace{-8pt}
%     \resumeProjectHeading
%       {\textbf{Connery} $|$ \emph{Deep learning} $|$ \texttt{ML.NET, ASP.NET Core}}{GitHub: \href{https://github.com/maacpiash/Connery}{\underline{Connery} \ExternalLink}}
%       \resumeItemListStart
%         \resumeItem{Fruit image classifier using convolutional neural networks.}
%         \resumeItem{Status: complete, offline.}
%       \resumeItemListEnd
%       \vspace{-8pt}
%     \resumeProjectHeading
%       {\textbf{Winston} $|$ \emph{Machine learning} $|$ \texttt{C, CMake, vcpkg}}{GitHub: \href{https://github.com/maacpiash/Winston}{\underline{Winston} \ExternalLink}}
%       \resumeItemListStart
%         \resumeItem{Implementation of neural networks from scratch.}
%         \resumeItem{Status: in progress.}
%       \resumeItemListEnd
%       \vspace{-8pt}
%     \resumeProjectHeading
%       {\textbf{Vardict} $|$ \emph{Library, Package} $|$ \texttt{Node.js}}{\href{https://www.npmjs.com/package/vardict}{\underline{NPM package} \ExternalLink} $|$ GitHub: \href{https://github.com/maacpiash/Vardict}{\underline{Vardict} \ExternalLink}}
%       \resumeItemListStart
%         \resumeItem{CLI argument parser.}
%         \resumeItem{Status: completed.}
%       \resumeItemListEnd
%   \resumeSubHeadingListEnd

% % -----------Open Source Contributions-----------
% \section{Open Source Contributions}
%   \begin{itemize}[leftmargin=0.75cm]
%     \item{\href{https://github.com/ubuntu-mate/ubuntu-mate.org/pull/141}{\underline{ubuntu-mate/ubuntu-mate.org\#141}}}
%     \item{\href{https://github.com/sandoche/Darkmode.js/pull/9}{\underline{sandoche/Darkmode.js\#9}}}
%     \item{\href{https://github.com/howtocode-dev/git.howtocode.dev/pull/21}{\underline{howtocode-dev/git.howtocode.dev\#21}}}
%     \item{\href{https://github.com/NetDevPack/Security.Jwt/pull/44}{\underline{NetDevPack/Security.Jwt\#44}}}
%   \end{itemize}
% \vspace{-16pt}

% -----------Publications-----------
\section{Publications}
 \begin{itemize}[leftmargin=0em, label={}]
    \item{
      Rahman, N.S.M.R., \textbf{Chowdhury, M.A.A.}, Siraj, AA.N., Rahman, R.M., Karim, R., \& Alam, K.M.A. (2018). Selection of Most Suitable Secondary School Alternative by Multi-Criteria Fuzzy Analytic Hierarchy Process. \textit{Multimedia and Network Information Systems}, 279–289. doi:10.1007/978-3-319-98678-4\_29. \href{https://link.springer.com/chapter/10.1007/978-3-319-98678-4_29}{\underline{link} \ExternalLink}}
    \item{
      Ashraf, S., Kadery, I., \textbf{Chowdhury, M.A.A.}, Mahbub, T.Z., \& Rahman, R.M. (2019). Fruit Image Classification by Convolutional Neural Networks. \textit{International Journal of Software Innovation (IJSI), 7}(4), 51–70. doi:10.4018/ijsi.2019100103. \href{https://www.igi-global.com/gateway/article/236206}{\underline{link} \ExternalLink}}
    \item{
      Rahman, N.S.M.R., \textbf{Chowdhury, M.A.A.}, Firoze, A., \& Rahman, R.M. (2024). Fusion of BWM and AHP MCDM Methods to Choose the Most Suitable Secondary School for an Individual in Context of Bangladesh. \textit{Vietnam Journal of Computer Science, 06}(03), 311–328. doi:10.1142/s2196888819500167. \href{https://www.worldscientific.com/doi/abs/10.1142/S2196888819500167}{\underline{link} \ExternalLink} \\
    }
 \end{itemize}

%-----------References-----------
\section{References}
Available on request.

\end{document}
