%-------------------------
% Resume in Latex
%------------------------
\documentclass[letter-paper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\lfoot{\vspace{5}Last updated on \today. Latest version of this document can be found at \href{https://pia.sh/resume}{\underline{pia.sh/resume}}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeItemWithoutHeading}[1]{
  \item\small{
    {#1 \vspace{-4pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{ #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  {\large \textbf{\textsc{Mohammad Abdul Ahad Chowdhury}}}\titlerule & Mobile: +61482605155\\
  11/53 Constitution Road, Meadowbank, NSW 2114 & Email: \href{mailto:ahad@maacpiash.com}{ahad@maacpiash.com}\\
  \href{https://www.maacpiash.com/}{www.maacpiash.com} & Skype: \href{https://join.skype.com/invite/UVzqFuCFERPh}{\underline{maacpiash}}\\
  LinkedIn: \href{https://linkedin.com/in/maacpiash}{https://linkedin.com/in/maacpiash} & GitHub: \href{https://github.com/maacpiash}{https://github.com/maacpiash}\\
\end{tabular*}

\section{Profile Summary}
Bangladeshi graduate student of data science, with one year of full-time professional experience in full-stack web development. Polyglot programmer, problem solver, team player. Adept at developing high-performance cloud-native web applications using ASP.NET Core and MERN-stack. Proficient in building solutions with machine learning and deep learning frameworks. Currently looking for a part-time, contract, or casual employment in the IT industry.


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Macquarie University}{Sydney, NSW, Australia}
      {Master of Data Science}{February 2020 -- May 2022}

      \newline
      Coursework: \href{https://github.com/maacpiash/COMP6200}{Data Science}, \href{https://github.com/maacpiash/COMP6210}{Big Data}, \href{https://github.com/maacpiash/COMP8220}{Machine Learning}
      
    \resumeSubheading
      {North South University}{Dhaka, Bangladesh}
      {Bachelor of Science in Computer Science and Engineering}{January 2014 -- August 2018}
      
      Capstone project: Fruit Image Classification Using Convolutional Neural Networks
      \newline
      Coursework: \href{https://github.com/maacpiash/CSE440}{Artificial Intelligence}, \href{https://github.com/maacpiash/CSE470}{Theory of Fuzzy Systems}, \href{https://github.com/maacpiash/CSE327}{Software Engineering}, \href{https://github.com/maacpiash/CSE331}{Microprocessor Interfacing \& Embedded System}, \href{https://github.com/maacpiash/SpaceShooter}{Computer Graphics}
  \resumeSubHeadingListEnd


%-----------WORK EXPERIENCE-----------------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Dynamic Solution Innovators Ltd.}{Dhaka, Bangladesh}
      {Junior Software Engineer}{February 2019 -- January 2020}
      
      Full-time employment working on Node.js-based full-stack (React.js and Hapi.js) web applications: the \href{https://opencrvs.org}{\underline{OpenCRVS}} project, and the enterprise solution of \href{https://olwel.com}{\underline{Olwel}}, a healthcare startup. Agile methodology (scrum) was followed.
      \newline
      \textbf{Responsibilities}: Added features and components; fixed bugs; optimized API calls and database queries; wrote database migration scripts; wrote unit tests. [View the commits for OpenCRVS on GitHub \href{https://github.com/opencrvs/opencrvs-core/commits?author=maacpiash}{\underline{here}}]
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {North South University}{Dhaka, Bangladesh}
      {Research Assistant}{November 2016 -- April 2018}
      
      Part-time employment under the Department of Environmental Science and Management. (\href{http://www.ipsnews.net/2017/05/flying-green-in-bangladesh/}{\underline{relevant news article}})
      \newline
      \textbf{Responsibility}: Developed the front-end software (Windows Forms) of NODES, an airline management system.
     
  \resumeSubHeadingListEnd
  
  %-----------Technical Skills-----------------
\section{Technical Skills}
  \resumeSubHeadingListStart
    \resumeSubItem{Programming languages}
      {C\#, JavaScript (ES6), TypeScript, Python, C, Java, C++, R}
    \resumeSubItem{Web development}
      {ASP.NET Core, Entity Framework Core, SignalR, Blazor, Node.js, Express.js, Hapi.js, Nest.js, React.js, Next.js, Vue.js, Angular (2+), Webpack, PWA, ReST, GraphQL, Socket.IO, Microservices architecture}
    \resumeSubItem{Machine learning \& data science}
      {Jupyter Notebook, NumPy, Pandas, NLTK, Scikit-Learn, ML.NET}
    \resumeSubItem{Desktop app development}
      {Windows Forms, WPF, UWP, Electron.js, JavaFX}
    \resumeSubItem{Database systems}
      {MongoDB, MySQL, Microsoft SQL Server, PostgreSQL, SQLite, RethinkDB}
    \resumeSubItem{DevOps}
      {Docker, Heroku, Azure App Service, MongoDB Atlas, basic CI/CD}
  \resumeSubHeadingListEnd

\vspace{-3pt}

%-----------PROJECTS-----------------
\section{Personal Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{KonSchool}
      {Fuzzy-AHP-based recommendation system for secondary schools in Bangladesh. -- ASP.NET Core, Docker, MongoDB [\href{https://github.com/maacpiash/KonSchool}{\underline{GitHub}} • \href{https://konschool.azurewebsites.net/}{\underline{Azure}} • \href{https://konschool.herokuapp.com}{\underline{Heroku}} • \href{https://hub.docker.com/r/maacpiash/konschool}{\underline{Docker}}]}
    \resumeSubItem{Connery}
      {Fruit-image-classifier using convolutional neural networks. -- ML.NET, ASP.NET Core [\href{https://github.com/maacpiash/Connery}{\underline{GitHub}} • \href{https://connery-api.herokuapp.com}{\underline{API Swagger}}]}
    \resumeSubItem{AddLicenseHeader}
      {A CLI tool that adds a license header on top of source files. -- .NET Core [\href{https://github.com/maacpiash/addlh}{\underline{GitHub}} • \href{https://www.nuget.org/packages/AddLicenseHeader}{\underline{NuGet package}}]}
    \resumeSubItem{Vardict}
      {A basic Node.js package for parsing labeled CLI arguments. -- Node.js, TypeScript [\href{https://github.com/maacpiash/vardict}{\underline{GitHub}} • \href{https://www.npmjs.com/package/vardict/}{\underline{NPM package}}]}
    \resumeSubItem{Prospect}
      {An app for reading the latest posts from popular coding blogs. \textit{WIP} -- Node.js, TypeScript, React.js, Next.js, Nest.js, PostgreSQL, GraphQL, Docker [\href{https://github.com/maacpiash/Prospect}{\underline{GitHub}}]}
  \resumeSubHeadingListEnd
  
\vspace{-3pt}

  %-----------Publication-----------------
\section{Publication}
  \resumeSubHeadingListStart
    \resumeItemWithoutHeading
      {Rahman, N. S. M. R., \textbf{Chowdhury, M. A. A.}, Siraj, A.-A. N., Rahman, R. M., Karim, R., & Alam, K. M. A. (2018). \textbf{Selection of Most Suitable Secondary School Alternative by Multi-Criteria Fuzzy Analytic Hierarchy Process.}  In: Choroś K., Kopel M., Kukla E., Siemiński A. (eds) Multimedia and Network Information Systems, 279-289. MISSI 2018. Advances in Intelligent Systems and Computing, vol 833. Springer, Cham. \href{https://link.springer.com/chapter/10.1007\%2F978-3-319-98678-4_29}{https://doi.org/10.1007/978-3-319-98678-4\_29}}

    \resumeItemWithoutHeading
      {Ashraf, S., Kadery, I., \textbf{Chowdhury, M. A. A.}, Mahbub, T. Z., & Rahman, R. M. (2019). \textbf{Fruit Image Classification Using Convolutional Neural Networks.} International Journal of Software Innovation, 7(4), 51–70. \href{https://www.igi-global.com/gateway/article/236206}{https://doi.org/10.4018/ijsi.2019100103}}
      
    \resumeItemWithoutHeading
      {Rahman, N. S. M. R., \textbf{Chowdhury, M. A. A.}, Firoze, A., & Rahman, R. M. (2019). \textbf{Fusion of BWM and AHP MCDM Methods to Choose the Most Suitable Secondary School for an Individual in the Context of Bangladesh.} Vietnam Journal of Computer Science, 06(03), 311–328. \href{https://www.worldscientific.com/doi/abs/10.1142/S2196888819500167}{https://doi.org/10.1142/s2196888819500167}}
  \resumeSubHeadingListEnd

\end{document}
