\cvsection{TECHNICAL SKILLS}
\cvtag{C\#}
\cvtag{JavaScript}
\cvtag{TypeScript}
\cvtag{Python}
\cvtag{SQL}
\cvtag{R}
\cvtag{C}
\cvtag{.NET Core}
\cvtag{ASP.NET Core}
\cvtag{Entity Framework Core}
\cvtag{Node.js}
\cvtag{Express.js}
\cvtag{React.js}
\cvtag{Redux.js}
\cvtag{Next.js}
\cvtag{Solid.js}
\cvtag{Astro}
\cvtag{Blazor}
\cvtag{PWA}
\cvtag{Electron.js}
\cvtag{Windows Forms}
\cvtag{WPF}
\cvtag{UWP}
\cvtag{Jupyter Notebook}
\cvtag{NumPy}
\cvtag{SciPy}
\cvtag{Pandas}
\cvtag{Matplotlib}
\cvtag{NLTK}
\cvtag{Keras}
\cvtag{Scikit-Learn}
\cvtag{Tensorflow}
\cvtag{ML.NET}
\cvtag{PostgreSQL}
\cvtag{MongoDB}
\cvtag{Redis}
\cvtag{Docker}
\cvtag{CI/CD}
\cvtag{PaaS}
\cvtag{IaaS}\\
%\divider
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Personal Projects}
\cvproject{KonSchool}
\begin{itemize}
\item Fuzzy-AHP-based recommendation system for secondary schools in Bangladesh.
\item Tech-stack: ASP.NET Core (Web API, Razor pages), MongoDB.
\item Status: Completed, with unit and e2e tests (xUnit and Moq) at 95\% coverage.
\begin{itemize}
    \item Another version is in development, with separate web APIs and a front-end developed with Blazor.
\end{itemize}
\item Categories: Web application.
\item Links: \href{https://github.com/maacpiash/KonSchool}{\underline{GitHub repository}}, Hosted on  \href{https://konschool.azurewebsites.net/}{\underline{Azure}} and \href{https://konschool.herokuapp.com}{\underline{Heroku}}, \href{https://hub.docker.com/r/maacpiash/konschool}{\underline{Docker image}}
\end{itemize}
\smallskip
\cvproject{Connery}
\begin{itemize}
\item Classifier of images of fruits that uses convolutional neural networks.
\item Tech-stack: ML.NET, ASP.NET Core.
\item Status: Completed, fixing bugs now.
\item Categories: Web application, Machine learning, Deep learning
\item Links: \href{https://github.com/maacpiash/Connery}{\underline{GitHub repository}}
\end{itemize}
\smallskip
\cvproject{Winston}
\begin{itemize}
\item Implementation of neural networks from scratch.
\item Tech-stack: C, CMake.
\item Status: In development (early stage)
\item Categories: Machine learning, Deep learning
\item Links: \href{https://github.com/maacpiash/Winston}{\underline{GitHub repository}}
\end{itemize}
\smallskip
% \cvproject{addlh}
% \begin{itemize}
% \item A CLI tool that adds a license header on top of each source file of a directory.
% \item Tech-stack: .NET Core.
% \item Status: In development
% \item Categories: CLI tool, Developer tool
% \item Links: \href{https://www.nuget.org/packages/AddLicenseHeader}{\underline{Nuget package}}, \href{https://github.com/maacpiash/addlh}{\underline{GitHub repository}}
% \end{itemize}
% \cvproject{}
